---
title: "ext_meta_id"
format:
  html:
    grid:
      body-width: 900px
    toc: true
    toc-depth: 2
    code-fold: true
    code-tools: true
---

## QC Summary

```{r}
#| echo: false
#| message: false
#| warning: false

library(tidyverse)
library(gt)

karyotype_tsv <- "ext_karyotype_tsv"
kary <- read_tsv(karyotype_tsv, show_col_types = FALSE)

qc_flag <- kary$qc_flag[1]

cat("### QC Status\n\n")

if (qc_flag == "pass") {
    cat("🟢 PASS (unexpected in skipped report)\n\n")
} else if (startsWith(qc_flag, "skipped")) {
    cat(paste0("🟡 SKIPPED — ", qc_flag, "\n\n"))
} else if (startsWith(qc_flag, "flagged")) {
    cat(paste0("🔴 FLAGGED — ", qc_flag, "\n\n"))
} else {
    cat(paste0("⚠️ UNKNOWN QC FLAG — ", qc_flag, "\n\n"))
}
```

## Karyotype Summary

```{r}
#| echo: false

kary %>%
    select(any_of(c("individual", "karyotype", "karyotype_conf", 
                    "x_copies", "y_copies", "chrX_ratio", 
                    "chrY_ratio", "auto_mean_cov"))) %>%
    gt() %>%
    tab_header(
        title = gt::md("**Inferred Karyotype**"),
        subtitle = "Coverage-based inference"
    )
```

## Coverage Plot

```{r}
#| echo: false

knitr::include_graphics("ext_karyotype_plot")
```

### Genome coverage profile

This plot shows the windowed sequencing coverage across chr18, chr21, chrX and chrY in 1Mb windows, allowing visual inspection of coverage uniformity and any large structural abnormalities.

```{r}
#| label: karyotype-genome-coverage
#| echo: false
#| fig-cap: "Genome coverage profile across chromosomes."

genome_cov_plot <- sub("_coverage_ratios\\.png$", "_genome_coverage.png", "ext_karyotype_plot")

if (file.exists(genome_cov_plot)) {
    knitr::include_graphics(genome_cov_plot)
} else {
    cat("Genome coverage plot not available.")
}
```

### RX vs RY

This scatter plot shows the chrX/autosome (RX) and chrY/autosome (RY) coverage ratios for this individual. The position of the point relative to the labelled karyotype regions allows visual confirmation of the inferred karyotype.

```{r}
#| label: karyotype-rx-ry
#| echo: false
#| fig-cap: "RX vs RY coverage ratio scatter plot."

rx_ry_plot <- sub("_coverage_ratios\\.png$", "_rx_ry.png", "ext_karyotype_plot")

if (file.exists(rx_ry_plot)) {
    knitr::include_graphics(rx_ry_plot)
} else {
    cat("RX vs RY plot not available.")
}
```

## Xp vs Xq Arm Check

```{r}
#| echo: false

xp_xq_plot <- sub("\\.png$", "_xp_xq.png", "ext_karyotype_plot")

if (file.exists(xp_xq_plot)) {
    knitr::include_graphics(xp_xq_plot)
} else {
    cat("Xp/Xq plot not available.")
}
```

## Interpretation

```{r}
#| echo: false

cat("This sample was excluded from downstream analysis.\n\n")

if (startsWith(qc_flag, "skipped")) {
    cat("Reason: insufficient quality or coverage for reliable phasing/skew analysis.\n")
} else if (startsWith(qc_flag, "flagged")) {
    cat("Reason: abnormal chromosomal signal detected (requires investigation).\n")
}
```
